\documentclass[11pt,a4paper]{article}
\usepackage{parskip}
\usepackage{bibentry}
\input resume-config

% ------------------------------------------------------------------
% Put username on front page nicely
% Arg 1 - your name    (e.g. 'Ajay Shah')
% Arg 2 - homepage URL (e.g. 'http://www.igidr.ac.in/\string~ajayshah')
%                            just saying blah/~ajayshah won't work!
% Arg 3 - your email address
\newcommand{\username}[3]{
  \hfill\begin{tabular}{r}
        \textbf{\LARGE \myhref{#2}{#1}} \\
        \hline
        \texttt{#3} \\
        \texttt{#2} \\
        \end{tabular}
}
% ------------------------------------------------------------------

% ------------------------------------------------------------------
% Setup new style for section/subsection titles
% Stolen from `The Latex Companion'
\makeatletter
\renewcommand\section{\@startsection {section}{1}{\z@}%
                              {-3.5ex \@plus -1ex \@minus -.2ex}%
                              {2.3ex \@plus.2ex}%
                              {\normalfont\large\bfseries\sffamily}}
\renewcommand\subsection{\@startsection{subsection}{2}{\z@}%
                                {-3.25ex\@plus -1ex \@minus -.2ex}%
                                {1.5ex \@plus .2ex}%
                                {\normalfont\large\sffamily}}
\renewcommand\subsubsection{\@startsection{subsubsection}{3}{\z@}%
                                {-3.25ex\@plus -1ex \@minus -.2ex}%
                                {1.5ex \@plus .2ex}%
                                {\normalfont\sffamily}}
\makeatother
% ------------------------------------------------------------------

\begin{document}
\sloppy
\bibliographystyle{plain}
\nobibliography{allmine}
\username{Ila Patnaik}
         {http://openlib.org/home/ila}
         {ilapatnaik@gmail.com}



\section*{Personal}

% Item 0
RBI Chair Professor, \\ National Institute of Public Finance and Policy, \\ 18/2 Satsang Vihar Marg, \\ Special Institutional Area, \\ New Delhi 110067.



\section*{Positions}

% Item 1
RBI Chair Professor, National Institute of Public Finance and Policy, New Delhi, October 2013 onwards.

% Item 2
Professor, National Institute of Public Finance and Policy, New Delhi, 2006 onwards.

% Item 3
Non-resident Senior Associate, South Asia Program, Carnegie Endowment for International Peace, Washington D.C., 2013.

% Item 4
Visiting Scholar, Research Department, IMF, Washington, D.C.: February-March 2013, October-November 2013, January-February 2003

% Item 5
Economics Editor, Indian Express, New Delhi, 2004 -- 2006.

% Item 6
Senior Fellow, Indian Council for Research in International Economic Relations, New Delhi, 2002 -- 2004.

% Item 7
Senior Economist, National Council of Applied Economic Research, New Delhi, 1996 -- 2002 and 2004.



\section*{Education}

% Item 12
Ph.D. in Economics, University of Surrey, Guildford, U.K., 1996.

% Item 13
M.Phil. in Economics, Centre for Economic Studies and Planning, Jawaharlal Nehru University, New Delhi, 1989.

% Item 14
M.A. in Economics, Centre for Economic Studies and Planning, Jawaharlal Nehru University, New Delhi, 1987.

% Item 15
B.A. in Economics, Hindu College, University of Delhi, Delhi, 1985.



\section*{Awards}

% Item 21
\textit{British Nehru Centenary Fellowship for Doctoral study in Economics in the UK}, 1991.

% Item 22
\textit{Junior Research Fellowship for Economics}, 1987.

% Item 23
\textit{National Talent Search Scholarship}, 1980.

% Item 24
\textit{Junior Science Talent Scholarship}, 1978.



\section*{Public policy}

% Item 16
Co-lead the Research Team that supported the \textit{Financial Sector Legislative Reforms Commission} chaired by Justice Srikrishna, Ministry of Finance, 2011-2013.

% Item 17
Co-lead the NIPFP-DEA Research Program for the Department of Economic Affairs, Ministry of Finance, 2007--2013. This includes: {\footnotesize \begin{enumerate} \item Producing new knowledge for Indian macroeconomic and financial policy. \item Supporting requests for policy support from DEA. \item Regular presentations at North Block about current policy issues. \item Running two international conferences per year. \end{enumerate}}

% Item 18
Member, Ministry of Finance \textit{Working Group on Foreign Investment}, Chaired by U. K. Sinha, 2009-10.

% Item 19
Member, Ministry of Finance \textit{Internal Working Group on Internal Debt Management}, Chaired by Jahangir Aziz, 2008.

% Item 20
Member, RBI Working Group on Economic Indicators, 2001-2002.



\section*{Media activities}

% Item 25
Columnist for \textit{Indian Express} and \textit{Financial Express}. Prior to this, columnist for \textit{Business Standard} (2000-2004).

% Item 26
Weekly television show \textit{Policy with Patnaik} on NDTV Profit, ran for two seasons of 13 weeks each, 2008-2009.



\section*{Work on business cycles}

% Item 27
\bibentry{Bhattacharyaetal2013_FPAS} 

% Item 28
\bibentry{PunditBhattacharyaPatnaik2013_financialIntegration}  \pdffile{PunditBhattacharyaPatnaik2013_financialIntegration.pdf}

% Item 29
\bibentry{BhattacharyaPatnaik2013_creditConstraints}  \pdffile{BhattacharyaPatnaik2013_creditConstraints.pdf}

% Item 30
\bibentry{GPS2012_stylisedfacts}  \pdffile{GPS2012_stylisedfacts.pdf}

% Item 31
\bibentry{JPS2009_decoupling}  \pdffile{JPS2009_decoupling.pdf}

% Item 32
\bibentry{PatnaikSharma2002_bci}  \pdffile{PatnaikSharma2002_bci.pdf}

% Item 33
\bibentry{Patnaik1997_ael}  \pdffile{Patnaik1997_ael.pdf}

% Item 34
\bibentry{SP2010_stabilising}  \pdffile{SP2010_stabilising.pdf}



\section*{Work on international finance}

% Item 35
\bibentry{PatnaikShahSingh2013_foreignInvestors}  \pdffile{PatnaikShahSingh2013_foreignInvestors.pdf}

% Item 36
\bibentry{PatnaikShah_institutionalInvestors}  \pdffile{PatnaikShah_institutionalInvestors.pdf}

% Item 37
\bibentry{PatnaikShah2012_capital_controls_worked}  \pdffile{PatnaikShah2012_capital_controls_worked.pdf}

% Item 38
\bibentry{PSS2012_misinvoicing}  \pdffile{PSS2012_misinvoicing.pdf}

% Item 39
\bibentry{SP2011_decomposition}  \pdffile{SP2011_decomposition.pdf}

% Item 40
\bibentry{PS2009_indiachoked}  \pdffile{PS2009_indiachoked.pdf}

% Item 41
\bibentry{PatnaikVasudevan2000_capitalflight}  \pdffile{PatnaikVasudevan2000_capitalflight.pdf}

% Item 42
\bibentry{ShahPatnaik2010_managing_capital_flows}  \pdffile{ShahPatnaik2010_managing_capital_flows.pdf}

% Item 43
\bibentry{ShahPatnaik2006_cflows} 

% Item 53
\bibentry{Guptaetal2013_LearningByExporting}  \pdffile{Guptaetal2013_LearningByExporting.pdf}

% Item 54
\bibentry{DemirbasPatnaikShah_graduatingGlobalisation}  \pdffile{DemirbasPatnaikShah_graduatingGlobalisation.pdf}

% Item 55
\bibentry{BPS2012_ymh}  \pdffile{BPS2012_ymh.pdf}



\section*{Work on exchange rates}

% Item 44
\bibentry{Patnaik2013_G20} 

% Item 45
\bibentry{PatnaikFelman2013_QE} 

% Item 46
\bibentry{PSSB2011_asia_err_crisis_to_crisis}  \pdffile{PSSB2011_asia_err_crisis_to_crisis.pdf}

% Item 47
\bibentry{ZSP2010_fxregime}  \pdffile{ZSP2010_fxregime.pdf}

% Item 48
\bibentry{PS2009_china_india_err} 

% Item 49
\bibentry{PS2010_err_changes_exposure}  \pdffile{PS2010_err_changes_exposure.pdf}

% Item 50
\bibentry{Patnaik2007_india_err} 

% Item 51
\bibentry{Patnaik2005_implementation}  \pdffile{Patnaik2005_implementation.pdf}

% Item 52
\bibentry{PatnaikPauly2001_indianforex}  \pdffile{PatnaikPauly2001_indianforex.pdf}



\section*{Work on macroeconomics}

% Item 56
\bibentry{PatnaikShah2012_asia_imp_trin} 

% Item 57
\bibentry{SP2010_india_fin_glob}  \pdffile{SP2010_india_fin_glob.pdf}

% Item 58
\bibentry{AcharyaAKP2006_indiacasestudy} 



% Skipped macro since there was nothing



\section*{Work on monetary policy}

% Item 59
\bibentry{PSV2011_measuring_inflation_India}  \pdffile{PSV2011_measuring_inflation_India.pdf}

% Item 60
\bibentry{BPS2008_earlywarnings}  \pdffile{BPS2008_earlywarnings.pdf}



\section*{Miscellaneous}

% Item 61
\bibentry{Patnaik2007_encyc_tariffs} 



\section*{Teaching}

% Item 8
Taught a course in International Economics at Indian Institute of Foreign Trade, 2004.

% Item 9
Lecturer, College of Vocational Studies, University of Delhi, Delhi, 1990-1991.

% Item 10
Lecturer, St. Stephen's College, University of Delhi, Delhi, 1989-1990.

% Item 11
Lecturer, Sri Venketeswara College, University of Delhi, Delhi, 1987-1988.
\end{document}
